BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-09-25 Paper/BOAST.tex
Improved Paper

\begin{lstlisting}
void magicfilter(int32_t n, int32_t ndat, const double * x, double * y){
}
\end{lstlisting}
\caption{BOAST Code Snippet for Procedure}
\label{fig:BOAST_procedure}
\end{figure}

@@

The generated outputs in FORTRAN~\ref{lst:BOAST_procedure_FORTRAN} and
C~\ref{lst:BOAST_procedure_C} show the difference in meta-information

@@

In this section we will present the different aspects of BOAST runtime that
allow this automation.

  \begin{itemize}
  \item multi target language generation ( performance, portability )
  \item compilation ( productivity, performance )
  \item execution ( productivity, performance )
  \item tracer, dumper and replay for non regression tests ( productivity )
  \end{itemize}

>>>>

\begin{lstlisting}
void magicfilter(const int32_t n, const int32_t ndat,
                 const double * x, double * y)
}
\end{lstlisting}
\caption{BOAST Code Snippet for Procedure}
\label{fig:BOAST_procedure}
\end{figure}

@@

The generated outputs in FORTRAN~\ref{lst:BOAST_procedure_FORTRAN} and
C~\ref{lst:BOAST_procedure_C} show the difference in meta-information that is
kept between both versions.

@@

In this section we will present the different aspects of BOAST runtime that
allow this automation. Those aspects are listed here:
  \begin{itemize}
  \item multi target language generation ( performance, portability )
  \item compilation ( productivity, performance )
  \item execution ( productivity, performance )
  \item tracer, dumper and replay for non regression tests ( productivity )
  \end{itemize}

  \subsubsection{Multi-target Language Generation}

Language availability and performance can vary between platforms. It is thus
important to be able to express computing kernels in different languages, based
on the availability and their respective merits on the target platform. Some
languages can have additional features, such as languages that target GPUs
(OpenCL, CUDA). The developer should be given tools to determine what kind of
language is currently used in order to be able to use those additional features.

Similarly the target language must be changed with ease in order to compare
different alternatives. Two methods are dedicated to this task: \emph{set\_lang}
and \emph{get\_lang}. The target language can also be set through environment
variable before launching BOAST, allowing for easy command line scripting.

  \subsubsection{Compilation}

Compilation of the generated kernels must also be very flexible. Indeed,

  \subsubsection{Execution}
  \subsubsection{Kernel Replay}
